Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry

### 2017-03-18 ms_pre_post.Rmd
Small change to generalise

When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H). Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B). Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D). In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations. Trajectories of $P_{a}$ values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp. S5-S12). Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.

>>>>

When post-copulatory inbreeding avoidance was allowed to evolve, mean $P_{a}$ values became substantially higher than in comparable simulations where $F_{a}$ values were fixed to zero and post-copulatory inbreeding avoidance could not evolve (Figure 1B,D,F,H). Allowing evolution of post-copulatory inbreeding avoidance alongside pre-copulatory inbreeding avoidance therefore facilitated evolution of polyandry to the degree that most females mated multiply given low costs of polyandry ($c_{P} < 0.005$; e.g., Figure 2A,B). Hence, given a low cost of polyandry, $P_{a}$ allele values increased from zero and persisted at low positive values (Figure 1B,D). In contrast, highers cost of polyandry ($c_{P} \geq 0.005$) resulted in initial increases of $P_{a}$ allele values from zero, but then became slightly negative over generations. Trajectories of allele values in individual simulations were typically highly stochastic, but also consistent in long-term direction (Supporting Information pp. S5-S12). Overall, this implies that, even given strong inbreeding depression in offspring viability, inbreeding avoidance might generally be a weak force driving polyandry evolution.
